Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-21 paper/paper.tex
Update paper.tex
change

\begin{table}
  \caption{Survey of Existing AutoML Frameworks}
  \label{automl-survey}
  \centering
  \begin{tabular}{lllllllll}
    \toprule
    Framework & EOU & Algs & FE & TM & HPT & Inter & Custom\\
    \midrule
    H2O AutoML & Easy & 6 & Basic & Yes & Auto & SHAP & High\\
    TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
    MLJAR & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
    FLAML & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
    LightAutoML & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, Algs: Algorithm Types, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
\end{table}
Table 1: Comparison of six AutoML frameworks based on commonmly evaluated criteria as well as more obscure features relevant to the medical diagnosis process

>>>>

\begin{table}
  \caption{Survey of Existing AutoML Frameworks}
  \label{automl-survey}
  \centering
  \begin{tabular}{lllllllll}
    \toprule
    Framework & EOU & M & FE & TM & HPT & Inter & Custom\\
    \midrule
    H2O AutoML & Easy & 6 & Basic & Yes & Auto & SHAP & High\\
    TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
    MLJAR & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
    FLAML & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
    LightAutoML & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, M: \# of models evaluated by framework, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
\end{table}
Table 1: Comparison of six AutoML frameworks based on commonmly evaluated criteria as well as more obscure features relevant to the medical diagnosis process
